A large leading tail of atmospheric escape in the HAT-P-67 b system

### 2023-03-09 paper/paper1/ms.tex
Add the Thorngren & Fortney reference
Ignore the Murray-Clay schematic, we probably will not use it

\begin{figure*}[t]
    \includegraphics[width=\linewidth]{figures/murray_clay_schematic_v0p2.png}
    \caption{Schematic of the relevant length scales in a stratified atmosphere, modeled after Figure 8 from \citet{2009ApJ...693...23M}.  The sonic point resides at a mere 2 atmospheric scale heights, and well below the photoionization level of Hydrogen, raising the possibility that the supersonic flow begins neutral and becomes ionized later on.}
    \label{fig:murrayClaySchematic}
\end{figure*}

>>>>

%\begin{figure*}[t]
%    \includegraphics[width=\linewidth]{figures/murray_clay_schematic_v0p2.png}
%    \caption{Schematic of the relevant length scales in a stratified atmosphere, modeled after Figure 8 from \citet{2009ApJ...693...23M}.  The sonic point resides at a mere 2 atmospheric scale heights, and well below the photoionization level of Hydrogen, raising the possibility that the supersonic flow begins neutral and becomes ionized later on.}
%    \label{fig:murrayClaySchematic}
%\end{figure*}
